---
title: "Offline Climpart Instructions"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)
```

## Step 1: Install Required Software
[R Programming Language](https://www.r-project.org)    
[R Studio IDE](https://www.rstudio.com)  
[GDAL](http://www.gdal.org) ([Windows Install](https://sandbox.idre.ucla.edu/sandbox/tutorials/installing-gdal-for-windows),
[MacOS Install Part 1](https://brew.sh), [MacOS Install Part 2](https://trac.osgeo.org/gdal/wiki/BuildingOnMac))
 

## Step 2: Install R Packages
After installing the required software, open R Studio and run the following to install the required R package dependencies:

```{r, eval= FALSE }
install.packages(
  c("rgdal","rgeos","raster","sp","shiny",
    "gdalUtils","data.table","leaflet",
    "shinycssloaders","htmlwidgets","tidyverse",
    "shinyalert")
)
```

## Step 3: Download Climate Data
Download the climateMerc.tif.zip from [this location](https://drive.google.com/open?id=1Ds5LuUiTknXlGiR3hl8VB28O8RvfFnNd), then unzip the contents to your working directory. Run the following to check if the file is in your working directory:

```{r, eval = F}
file.exists('climateMerc.tif')
```

## Step 4: Execute the Source Code for the App
Run the following commands in R Studio to load the app:

```{r, eval = FALSE}

#Github repository for the server script
source('https://raw.githubusercontent.com/mosscoder/climpart/master/server.R')

#Github repository for the UI script
source('https://raw.githubusercontent.com/mosscoder/climpart/master/ui.R')

shinyApp(ui = ui, server = server,
         onStart = function(){
           rasterOptions(maxmemory = 1e9)
           temp.folder <<-  tempdir()
         })
```



